\section*{Executive Summary}

For blockchain technology and digital currencies to achieve mainstream adoption, consumers require a scalable, high-performing messaging and payment platform that affirms and preserves a user's right to digital sovereignty, without compromising user experience---blockchain performance and convenience. The \name blockchain has been designed to address performance issues hindering the adoption of current decentralized systems, while maintaining the privacy consumers require.

\name provides users with:
\begin{itemize}
    \item \textbf{Speed}: Payment completion and message transmission are completed in a matter of seconds.
    \item \textbf{Transactional privacy}: Only senders and receivers can review and prove payment history. Transaction data is not stored on the blockchain.
    \item \textbf{Communication privacy}: The identity of communicating parties and their devices remains private.
\end{itemize}

The architecture of the \name platform provides users with performance that scales linearly as computers join the network. Network nodes are incentivized to maximize throughput while ensuring security, and payments use a faster hash-based ownership mechanism instead of digital signatures. 

The \name consensus requires nodes work in teams that are sequentially assigned the task of generating blocks as opposed to requiring all nodes to compete individually. Within teams, all nodes are required to independently create cryptographically verifiable proofs that are published alongside the new block, proving that transactions were received and processed properly. \name users are able to validate the integrity of transaction processing using these proofs. Additionally, the existence of just one honest node within the team is sufficient to preserve the anonymity of users. 

\name's privacy features are unique and novel capabilities in decentralized technology. Both users and distributed applications enjoy the benefits of a sophisticated anonymization protocol that enables private messaging and transactions. The platform does not store transactions on the blockchain, only tokens, further protecting user privacy.

The team behind the creation of \name is comprised of pioneers of practical, anonymous and verifiable cryptographic systems. Its members are among the first to propose and deploy digital currencies, mix networks, unpermissioned cryptography, anonymous user discovery, verifiable voting systems, and many other advances in cryptography. They have dedicated their collective decades of experience in this space to this breakthrough platform. 

\name is capable of replacing current centralized systems at scale and with quick response times. The \name platform targets game-changing verifiability, privacy, and digital sovereignty because, together, they are the digital future.
