\section{Introduction}

\name is a decentralized blockchain platform that allows users to communicate and exchange value securely and confidentially. \name's breakthrough design produces a decentralized network capable of potentially scaling to process transactions on a mega-tps scale, far exceeding the kilo-tps scale characteristic of conventional mainstream payment systems. The \name design provides users with a blockchain platform that achieves the kind of performance that consumers expect from current centralized systems:

\begin{enumerate}
    \item \textbf{Speed}: Payment processing on the order of seconds, from start to irrevocable finality.
    \item \textbf{Scale}: Tens of thousands of transactions per second.
    \item \textbf{True Privacy}: Transactions that are not linked to users or to other transactions. Communications are end-to-end encrypted, they can only be read by the intended recipients.
\end{enumerate}

\name has been designed to realize the vision of a world in which digital sovereignty truly exists, a world in which users can protect themselves and control their privacy by revealing only the absolute minimum amount of information necessary to conduct transactions. \name has been built for the user. Users generate and control their own keys. Users control access to all of their confidential interactions. Users have exclusive access to all their digital property. Users control linkage of any personal credentials to their data. Users are in control of their digital future.

Mainstream adoption of blockchain technology requires a platform capable of scaling to process the necessary high transaction volumes while protecting user's digital sovereignty. To that end, the \name team---led by Dr. David Chaum---has leveraged their experience as innovators in  blockchain technology, consensus mechanisms, unpermissioned cryptography, cryptocurrencies, and online voting to address this challenge through the creation of \name.

